### 2017-04-03 paper/evaluation.tex
adjustments
adjusting

To enforce sequential execution, \Luis{rework this $\rightarrow$} we 
analyzed the \numProjectsPar{} subjects looking for the parallelism 
configuration inside the \pomf{} of each module. To run the subjects
sequentially, we manually modified the Maven Surefire configuration
from the \numPomMatched{} identified before to not run in parallel.
The Figure~\ref{fig:surefire-configuration} show the injected configuration
in each \pomf{}.

\input{codes/surefire}

@@

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
      that parallelism features are underused given that only
	  \percentParallel{}
      of projects supports parallel execution of test suites.}
  \end{minipage}
}
\end{center}

@@

\Luis{rework this $\rightarrow$}
We considered the \numNonParallel{} subjects that do not use any
parallel mode from Section~\ref{sec:rqC} and elaborated a
quick survey to extent the comprehension about why developers do not
use parallel configuration. \Luis{describe how we created the survey}.
In total, we sent \emailsSent{} e-mails to developers that recently
contributed to the project and received \emailsAnswered{} answers.

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQE{}:~\emph{\Luis{summarize
	  findings...}}}
  \end{minipage}
}
\end{center}

>>>>

To enforce sequential execution, \Luis{rework this $\rightarrow$} we 
analyzed the \numProjectsPar{} subjects looking for the parallelism 
configuration inside the \pomf{} of each module. To run the subjects
sequentially, we manually modified the Maven Surefire configuration
from the \numPomMatched{} identified before to not run in parallel.

@@

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
      that parallelism features are underused by defailt given that only
	  \percentParallel{}
      of projects supports parallel execution of test suites without
	  any extra parameter.}
  \end{minipage}
}
\end{center}

@@

\Luis{rework this $\rightarrow$}
We considered the \numNonParallel{} subjects that do not use any
parallel mode from Section~\ref{sec:rqC-1} and elaborated a
quick survey to extent the comprehension about why developers do not
use parallel configuration. \Luis{describe how we created the survey}.
We first retrieve the last 20 commits from the project repository and
got the developers e-mails. In total, we sent \emailsSent{} e-mails to
different developers that recently contributed to the project.
There were \emailsAnswered{} replies, and \emailsTrueAnswers{} of
those were answering the survey.

The survey sent was composed by three open questions and one closed
question: (I) How long does it take for test to run in your
environment? Can you briefly define your setup? (II) Do you confirm
that your project does not run in parallel? (III) Select a reason for
not using parallelization: (a) I did not know it was possible; (b) I
was concerned with concurrency issues; (c) I use a continuous
integration server; (d) Some other reason. Please elaborate.

\Comment{
\begin{enumerate}
	\item How long does it take for test to run in your
		environment?
	\item Can you briefly define your setup?
	\item Do you confirm that your project does not run in
		parallel?
	\item Select a reason for not using paralellization:
		\begin{enumarate}
			\item I did not know it was possible;
			\item I was concerned with concurrency issues;
			\item I use a continuous integration server;
			\item Some other reason.
		\end{enumerate}
\end{enumerate}
}
\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQE{}:~\emph{\Luis{summarize
	  findings...}}}
  \end{minipage}
}
\end{center}
